Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-07-24 content.tex
Twinning does use birth_death by default, code also uses birth_death
Simulating alignments uses the same mutation rate

From the twin tree, we simulate an alignment following the same
history as the twin tree, with the constraint that 
the same total number of mutations have
taken place.
This constraint ensures there is the same amount of historical information
stored in both the true and twin alignments.
We achieve this by simply simulating twin alignments until we
obtain one that has the desired number of mutations.

@@

\begin{lstlisting}[
  language = R,
  floatplacement = ht,
  frame = single,
  label = {lst:create_twinning_params},
  caption = Create the default twinning parameters.
]
twinning_params <- create_twinning_params(
  twin_model = "yule",
  method = "random_tree"
)
\end{lstlisting}

>>>>

From the twin tree, we simulate an alignment following the same
history as the twin tree, using the same mutation rate,
with the constraint that 
the same total number of mutations have
taken place.
This constraint ensures there is the same amount of historical information
stored in both the true and twin alignments.
We achieve this by simply simulating twin alignments until we
obtain one that has the desired number of mutations.

@@

\begin{lstlisting}[
  language = R,
  floatplacement = ht,
  frame = single,
  label = {lst:create_twinning_params},
  caption = Create the default twinning parameters.
]
twinning_params <- create_twinning_params(
  twin_model = "birth_death",
  method = "random_tree"
)
\end{lstlisting}
